### 2022-02-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@3c227d502c51d6af7120b629e55d2607747bcc7f 🚀

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple; left side
matrix) and right (green/brown; top matrix) subspaces, alongside the
adjacency matrix of the food web they encode (greyscale). The European
metaweb is on the left, and the imputed Canadian metaweb (before data
inflation) on the right. This figure illustrates how much structure the
left subspace captures. As we show in fig.~\ref{fig:degree}, the species
with a value of 0 in the left subspace are species without any
prey.}\label{fig:subspaces}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:degree}{%
\centering
\includegraphics{figures/figure-degree.png}
\caption{Top: biological significance of the first dimension. Left:
there is a linear relationship between the values on the first dimension
of the left subspace and the generality, \emph{i.e.} the relative number
of preys, \emph{sensu} Schoener (1989). Species with a value of 0 in
this subspace are at the bottom-most trophic level. Right: there is,
similarly, a linear relationship between the position of a species on
the first dimension of the right subspace and its vulnerability,
\emph{i.e.} the relative number of predators. Taken together, these two
figures show that the first-order representation of this network would
capture its degree distribution. Bottom: topological consequences of the
first dimension. Left: differences in the \(z\)-score of the actual
configuration model for the reconstructed network, and the prediction
based only on the first dimension. Right: distribution of the
differences in the left panel.}\label{fig:degree}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple; left-side
matrix) and right (green/brown; top matrix) subspaces, alongside the
adjacency matrix of the food web they encode (greyscale). The European
metaweb is on the left, and the imputed Canadian metaweb (before data
inflation) on the right. This figure illustrates how much structure the
left subspace captures. As we show in fig.~\ref{fig:degree}, the species
with a value of 0 in the left subspace are species without any
prey.}\label{fig:subspaces}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:degree}{%
\centering
\includegraphics{figures/figure-degree.png}
\caption{Top: biological significance of the first dimension. Left:
there is a linear relationship between the values on the first dimension
of the left subspace and the generality, \emph{i.e.} the relative number
of preys, \emph{sensu} Schoener (1989). Species with a value of 0 in
this subspace are at the bottom-most trophic level. Right: there is,
similarly, a linear relationship between the position of a species on
the first dimension of the right subspace and its vulnerability,
\emph{i.e.} the relative number of predators. Taken together, these two
figures show that the first-order representation of this network would
capture its degree distribution. Bottom: topological consequences of the
first dimension. Left: differences in the \(z\)-scores of the actual
configuration model for the reconstructed network, and the prediction
based only on the first dimension. Right: distribution of the
differences in the left panel.}\label{fig:degree}
}
\end{figure}
